Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-05-31 GWLDCI.tex
created a bib file for paper 1

%\bibliographystyle{plain}
%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}

\begin{thebibliography}{50}

\bibitem{positroids13}
Federico Ardila, Felipe Rinc{\'{o}}n, and Lauren Williams.
\newblock Positroids and non-crossing partitions.
\newblock {\em Transactions of the American Mathematical Society}, 2015.
\newblock arXiv:1308.2698v2.

\bibitem{Adamo:2011pv}
Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
\newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
\newblock {\em J.Phys.A}, A44:454008, 2011.

\bibitem{wilsonloop}
Susama Agarwala and Eloi~Marin Amat.
\newblock Wilson loop diagrams and positroids.
\newblock {\em Communications in Mathematical Physics}, 2016.
\newblock arXiv:1509.06150.

\bibitem{casestudy}
Susama Agarwala and Si\^an Fryer.
\newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
  of {W}ilson loop diagrams and {SYM} $N=4$.
\newblock arXiv:1803.00958.

\bibitem{generalcombinatoricsI}
Susama Agarwala, Si\^an Fryer, and Karen Yeats.
\newblock Combinatorics of the geometry of {W}ilson loop diagrams {II}: {G}rassmann necklaces, dimensions, and denominators.
\newblock manuscript in progress.

\bibitem{non-orientable}
Susama Agarwala and Cameron Marcott.
\newblock Wilson loops in {SYM} $N=4$ do not parametrize an orientable space.
\newblock arXiv:1807.05397.

\bibitem{arkani:2012nw}
Nima Arkani-Hamed, Jacob~L. Bourjaily, Freddy Cachazo, Alexander~B Goncharov,
  Alexander Postnikov, and Jaroslav Trnka.
\newblock Scattering amplitudes and the positive {G}rassmannian.
\newblock arXiv:1212.5605, 2012.

\bibitem{Arkani-Hamed:2013kca}
Nima Arkani-Hamed and Jaroslav Trnka.
\newblock {Into the Amplituhedron}.
\newblock {\em JHEP}, 12:182, 2014.

\bibitem{Arkani-Hamed:2013jha}
Nima Arkani-Hamed and Jaroslav Trnka.
\newblock {The Amplituhedron}.
\newblock {\em JHEP}, 10:30, 2014.

\bibitem{Britto:2005fq}
Ruth Britto, Freddy Cachazo, Bo~Feng, and Edward Witten.
\newblock {Direct proof of tree-level recursion relation in Yang-Mills theory}.
\newblock {\em Phys.Rev.Lett.}, 94:181602, 2005.

\bibitem{Cachazo:2004kj}
Freddy Cachazo, Peter Svrcek, and Edward Witten.
\newblock {MHV vertices and tree amplitudes in gauge theory}.
\newblock {\em JHEP}, 0409:006, 2004.

\bibitem{Amplituhedronsquared}
Burkhard Eden, Paul Heslop, and Lionel Mason.
\newblock The correlahedron.
\newblock 2017.
\newblock arxiv:1701.00453.

\bibitem{galashinlam}
P.~{Galashin} and T.~{Lam}.
\newblock {Parity duality for the amplituhedron}.
\newblock {\em arXiv e-prints}, May 2018.

\bibitem{HeslopStewart}
Paul Heslop and Alastair Stewart.
\newblock The twistor {W}ilson loop and the amplituhedron.
\newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.

\bibitem{AmplituhedronDecomposition}
Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
\newblock Decompostions of amplituhedra.
\newblock arXiv:1708.09525.

\bibitem{Gale}
D. Gale.
\newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
\newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).

\bibitem{Oh}
S. Oh.
\newblock Positroids and {S}chubert matroids.
\newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)

\bibitem{Postnikov}
A.~Postnikov.
\newblock Total positivity, {G}rassmannians, and networks.
\newblock \url{arXiv:math/0609764}.

\bibitem{PSpolygon}
  J\'ozef H. Przytycki and Adam S. Sikora.
  \newblock Polygon dissections and {E}uler, {F}uss, {K}irkman and {C}ayley numbers.
  \newblock {\em J. Combin. Theory Ser. A}, 92(1):68--76, (2000). \url{arXiv:math/9811086}.

\bibitem{Stanley}
  R. P. Stanley.
  \newblock Enumerative Combinatorics, Vol. 2.
  \newblock Wadsworth (1999)

\bibitem{Ziegler}
  G. M. Ziegler.
  \newblock Lectures on Polytopes.
  \newblock Springer GTM 152, (1995)

\bibitem{OxleyMatroidBook}
James~G. Oxley.
\newblock {\em Matroid Theory}, volume~21 of {\em Oxford graduate texts in
  mathematics}.
\newblock Oxford University Press, New York, 2011.

\bibitem{CSZinequivalent}
  Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler.
  \newblock Many non-equivalent realizations of the associahedron
  \newblock {\em Combinatorica}, 35(5):513--551, (2015).  \url{arxiv:1109.5544}

\end{thebibliography}

>>>>

\bibliographystyle{abbrv}
\bibliography{WLDbib}

%\begin{thebibliography}{50}

% \bibitem{positroids13}
% Federico Ardila, Felipe Rinc{\'{o}}n, and Lauren Williams.
% \newblock Positroids and non-crossing partitions.
% \newblock {\em Transactions of the American Mathematical Society}, 2015.
% \newblock arXiv:1308.2698v2.

% \bibitem{Adamo:2011pv}
% Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
% \newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
% \newblock {\em J.Phys.A}, A44:454008, 2011.

% \bibitem{wilsonloop}
% Susama Agarwala and Eloi~Marin Amat.
% \newblock Wilson loop diagrams and positroids.
% \newblock {\em Communications in Mathematical Physics}, 2016.
% \newblock arXiv:1509.06150.

% \bibitem{casestudy}
% Susama Agarwala and Si\^an Fryer.
% \newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
%   of {W}ilson loop diagrams and {SYM} $N=4$.
% \newblock arXiv:1803.00958.

% \bibitem{generalcombinatoricsI}
% Susama Agarwala, Si\^an Fryer, and Karen Yeats.
% \newblock Combinatorics of the geometry of {W}ilson loop diagrams {II}: {G}rassmann necklaces, dimensions, and denominators.
% \newblock manuscript in progress.

% \bibitem{non-orientable}
% Susama Agarwala and Cameron Marcott.
% \newblock Wilson loops in {SYM} $N=4$ do not parametrize an orientable space.
% \newblock arXiv:1807.05397.

% \bibitem{arkani:2012nw}
% Nima Arkani-Hamed, Jacob~L. Bourjaily, Freddy Cachazo, Alexander~B Goncharov,
%   Alexander Postnikov, and Jaroslav Trnka.
% \newblock Scattering amplitudes and the positive {G}rassmannian.
% \newblock arXiv:1212.5605, 2012.

% \bibitem{Arkani-Hamed:2013kca}
% Nima Arkani-Hamed and Jaroslav Trnka.
% \newblock {Into the Amplituhedron}.
% \newblock {\em JHEP}, 12:182, 2014.

% \bibitem{Arkani-Hamed:2013jha}
% Nima Arkani-Hamed and Jaroslav Trnka.
% \newblock {The Amplituhedron}.
% \newblock {\em JHEP}, 10:30, 2014.

% \bibitem{Britto:2005fq}
% Ruth Britto, Freddy Cachazo, Bo~Feng, and Edward Witten.
% \newblock {Direct proof of tree-level recursion relation in Yang-Mills theory}.
% \newblock {\em Phys.Rev.Lett.}, 94:181602, 2005.

% \bibitem{Cachazo:2004kj}
% Freddy Cachazo, Peter Svrcek, and Edward Witten.
% \newblock {MHV vertices and tree amplitudes in gauge theory}.
% \newblock {\em JHEP}, 0409:006, 2004.

% \bibitem{Amplituhedronsquared}
% Burkhard Eden, Paul Heslop, and Lionel Mason.
% \newblock The correlahedron.
% \newblock 2017.
% \newblock arxiv:1701.00453.

% \bibitem{galashinlam}
% P.~{Galashin} and T.~{Lam}.
% \newblock {Parity duality for the amplituhedron}.
% \newblock {\em arXiv e-prints}, May 2018.

% \bibitem{HeslopStewart}
% Paul Heslop and Alastair Stewart.
% \newblock The twistor {W}ilson loop and the amplituhedron.
% \newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.

% \bibitem{AmplituhedronDecomposition}
% Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
% \newblock Decompostions of amplituhedra.
% \newblock arXiv:1708.09525.

% \bibitem{Gale}
% D. Gale.
% \newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
% \newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).

% \bibitem{Oh}
% S. Oh.
% \newblock Positroids and {S}chubert matroids.
% \newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)

% \bibitem{Postnikov}
% A.~Postnikov.
% \newblock Total positivity, {G}rassmannians, and networks.
% \newblock \url{arXiv:math/0609764}.

% \bibitem{PSpolygon}
%   J\'ozef H. Przytycki and Adam S. Sikora.
%   \newblock Polygon dissections and {E}uler, {F}uss, {K}irkman and {C}ayley numbers.
%   \newblock {\em J. Combin. Theory Ser. A}, 92(1):68--76, (2000). \url{arXiv:math/9811086}.

% \bibitem{Stanley}
%   R. P. Stanley.
%   \newblock Enumerative Combinatorics, Vol. 2.
%   \newblock Wadsworth (1999)

% \bibitem{Ziegler}
%   G. M. Ziegler.
%   \newblock Lectures on Polytopes.
%   \newblock Springer GTM 152, (1995)

% \bibitem{OxleyMatroidBook}
% James~G. Oxley.
% \newblock {\em Matroid Theory}, volume~21 of {\em Oxford graduate texts in
%   mathematics}.
% \newblock Oxford University Press, New York, 2011.

% \bibitem{CSZinequivalent}
%   Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler.
%   \newblock Many non-equivalent realizations of the associahedron
%   \newblock {\em Combinatorica}, 35(5):513--551, (2015).  \url{arxiv:1109.5544}

%\end{thebibliography}
